Object-Oriented Internet - Azure Interoperability

### 2020-12-10 Latex/Manuscript.tex
Middleware definition and ref #49
- Research Gate

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway archetype best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway archetype has been implemented as a composable part of a selected OPC UA PubSub framework.

@@

\begin{itemize}
      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the cyber-physical network
      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the cyber-physical network
      \item \textbf{embedded gateway} - a software part composed into a selected node of the cyber-physical network
\end{itemize}

\textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices. Additionally, it allows the selection of initial data processing and execution of them using local resources. The \textbf{edge device} may be located close to the leaf devices and attached to the cyber-physical network using protocols applicable only to local computer networks. In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing. In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.

The \textbf{field level gateway} is also build atop of the middleware\cite{Middleware-Sunyaev} concept. The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected. In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.

@@

Unlike the above described solutions, the \textbf{embedded gateway} is not derived from the middleware concept. A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

The \textbf{embedded gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few. The main goal of this article is to provide proof that the \textbf{embedded gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern. The proposed implementation is designed for selected interoperability standard and cloud product.

@@

\begin{itemize}
      \tightlist
      \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
      \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
\end{itemize}

@@

From the analysis covered by the Sect. \ref*{subs.architecture} it is concluded that the \textbf{embedded gateway} archetype best suits all requirements described above. It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e. \textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent. Additionally, it could be used to connect to many independent clouds at the same time. The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}. Main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \textbf{embedded gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.

>>>>

      Optimization of the industrial processes requires further research on the integration of machine-centric systems with human-centric cloud-based services in the context of new emerging disciplines, namely Industry 4.0 and Industrial Internet of Things. This research aims at working out a new generic architecture and deployment scenario applicable to this integration. The reactive interoperability relationship of the interconnected nodes is proposed to deal with the network traffic propagation asymmetry or assets' mobility. Described solution based on the OPC Unified Architecture international standard relaxes issues related to the real-time multi-vendor environment. The discussion addressing the generic architecture concludes that the embedded gateway software part best suits all requirements. To promote separation of concerns and reusability, the proposed architecture of the embedded gateway has been implemented as a composable part of a selected OPC UA PubSub framework.

@@

\begin{itemize}
      \item \textbf{edge device} - remote cloud agent acting as an intermediary for nodes of the CPS
      \item \textbf{field level gateway} - a dedicated custom agent acting as an intermediary for nodes of the CPS
      \item \emph{Embedded Gateway} - a software part composed into a selected node of the \emph{Cyber-physical network} (\ref*{figure1.StrategyDomainModel})
\end{itemize}

\textbf{Edge device} connects directly to the cloud services but acts as an intermediary for other devices called leaf devices. Additionally, it allows the selection of initial data processing and execution of them using local resources. The \textbf{edge device} may be located close to the leaf devices and attached to the \emph{Cyber-physical network} using protocols applicable only to local computer networks. In this scenario, it is possible to use a custom protocol stack to get connected to the \textbf{edge device} with the cloud and helps to save the bandwidth thanks to sending only the results of local processing. In this approach, the \textbf{edge device} is part of cloud vendor products and cannot be recognized as a generic solution that can be used to connect to other clouds at the same time.

The \textbf{field level gateway} is also build atop of the middleware\cite{Sunyaev2020} concept. The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected. In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.

@@

Unlike the above described solutions, the \emph{Embedded Gateway} is not derived from the middleware concept. A generic domain model for this interconnection is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. Promoting separation of concern design principle, the gateway functionality should be implemented as a self-contained software part embedded in the \emph{Networking} service of the \emph{Cyber-physical\ node}. Main functionality of this component is to transfer selected data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

The \emph{Embedded Gateway} archetype relaxes most of the issues described above: \emph{Cyber-physical\ network} real-time behavior, data encoding incompatibility, security-context differences to name only a few. The main goal of this article is to provide proof that the \emph{Embedded Gateway} archetype implementation is possible based on a generic architecture that can be used as a foundation for the integration of the heterogenous environments in concern. The proposed implementation is designed for selected interoperability standard and cloud product.

@@

\begin{itemize}
      \item \textbf{session-oriented}: requires a session that has to be established before any data can be sent between sender and receiver
      \item \textbf{sessionless-oriented}: the sender may start sending messages (called packets or datagrams) to the destination without any preceding handshake procedure
\end{itemize}

@@

From the analysis covered by the Sect. \ref*{subs.architecture} it is concluded that the \emph{Embedded Gateway} archetype best suits all requirements described above. It relaxes most of the issues related to \textbf{direct interconnection} and solutions inferred from the middleware concept, i.e. \textbf{edge device} - remote cloud agent and \textbf{field level gateway} - a dedicated custom agent. Additionally, it could be used to connect to many independent clouds at the same time. The generic domain model for the proposed interconnection archetype is presented in the Fig.~\ref*{figure1.StrategyDomainModel}. We have highlighted that to promote the separation of concern design principle, the gateway functionality should be implemented as a self-contained dedicated software part embedded in the core \emph{Networking} service of the \emph{Cyber-physical\ node}. Main functionality of this component is to transfer process data between \emph{Cyber-physical\ network} using \emph{Networking} services of an existing \emph{Cyber-physical\ node} and \emph{Cloud-based\ front-end} using officially supported by the cloud vendor interconnection services.

@@

The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
